Adversarial Variational Optimization\\ of Non-Differentiable Simulators

### 2018-07-20 colt/avo.tex
update code

\documentclass[12pt]{colt2018} % Anonymized submission
% \documentclass{colt2017} % Include author names

@@

    \begin{flushleft}
        {\it Inputs:} observed data $\{ \mathbf{x}_i \sim p_r(\mathbf{x}) \}_{i=1}^N$, simulator $g$.\\
        {\it Outputs:} proposal distribution $q(\bftheta|\bfpsi)$, such that $\qxpsi \approx p_r(\mathbf{x})$.\\
        {\it Hyper-parameters:} The number $n_{\text{critic}}$ of training iterations of $d$; the size $M$ of a mini-batch; the gradient penalty coefficient $\lambda$; the entropy penalty coefficient $\gamma$.
    \end{flushleft}

    \label{alg:avo}
    \begin{algorithmic}[1]
        \State{$q(\bftheta|\bfpsi) \leftarrow \text{prior on $\bftheta$ (with differentiable and known density)}$}
        \While{$\bfpsi$ has not converged}
            \For{$i=1$ to $n_{\text{critic}}$} \Comment{Update $d$}
                \State{Sample a mini-batch $\{\mathbf{x}_m \sim p_r(\mathbf{x}), \bftheta_m \sim q(\bftheta|\bfpsi), \bfz_m \sim p(\bfz|\bftheta_m), \epsilon_m \sim U[0,1] \}_{m=1}^M$.}
                \For{$m=1$ to $M$}
                    \State{$\tilde{\mathbf{x}}_m \leftarrow g(\bfz_m; \bftheta_m)$}
                    \State{$\hat{\mathbf{x}}_m \leftarrow \epsilon_m \mathbf{x}_m + (1 - \epsilon_m) \tilde{\mathbf{x}}_m$}
                    \State{$U_d^{(m)} \leftarrow d(\tilde{\mathbf{x}}_m; \bfphi) - d(\mathbf{x}_m; \bfphi) + \lambda (|| \nabla_{\hat{\mathbf{x}}_m} d(\hat{\mathbf{x}}_m; \bfphi) ||_2 - 1)^2 $}
                \EndFor
                \State{$\bfphi \leftarrow \text{Adam}(\nabla_\bfphi \tfrac{1}{M} \sum_{m=1}^M U_d^{(m)})$}
            \EndFor
            \State{Sample a mini-batch $\{ \bftheta_m \sim q(\bftheta|\bfpsi),  \bfz_m \sim p(\bfz|\bftheta_m) \}_{m=1}^M$.}  \Comment{Update $q(\bftheta|\bfpsi)$}
            \State{$\nabla_\bfpsi U_g \leftarrow \tfrac{1}{M} \sum_{m=1}^M -d(g(\bfz_m; \bftheta_m)) \nabla_\bfpsi \log q_\bfpsi(\bftheta_m)$}
            % \State{$\mathbf{F}(\bfpsi) \leftarrow \tfrac{1}{M} \sum_{m=1}^M  \nabla_\bfpsi \log q_\bfpsi(\bftheta_m) \nabla_\bfpsi \log q_\bfpsi(\bftheta_m)^{\top}$}
            \State{$\nabla_\bfpsi H(q_\bfpsi) \leftarrow \tfrac{1}{M} \sum_{m=1}^M  \nabla_\bfpsi q_\bfpsi(\bftheta_m) \log q_\bfpsi(\bftheta_m)$}
            \State{$\bfpsi \leftarrow \text{Adam}(\nabla_\bfpsi U_g + \gamma \nabla_\bfpsi H(q_\bfpsi))$}
        \EndWhile
    \end{algorithmic}
    \end{algorithm}
    \end{minipage}
\end{figure*}

>>>>

\documentclass[anon,12pt]{colt2018} % Anonymized submission
% \documentclass{colt2017} % Include author names

@@

    \begin{flushleft}
        {\it Inputs:} observed data $\{ \mathbf{x}_i \sim p_r(\mathbf{x}) \}_{i=1}^N$, simulator $g$.\\
        {\it Outputs:} proposal distribution $q(\bftheta|\bfpsi)$, such that $\qxpsi \approx p_r(\mathbf{x})$.\\
        {\it Hyper-parameters:} The number $n_{\text{critic}}$ of training iterations of $d$; the size $M$ of a mini-batch; the gradient penalty coefficient $\lambda_{GP}$; the entropy penalty coefficient $\gamma$.
    \end{flushleft}

    \label{alg:avo}
    \begin{algorithmic}[1]
        \State{$q(\bftheta|\bfpsi) \leftarrow \text{prior on $\bftheta$ (with differentiable and known density)}$}
        \While{$\bfpsi$ has not converged}
            \For{$i=1$ to $n_{\text{critic}}$} \Comment{Update $d$}
                \State{Sample a mini-batch $\{\mathbf{x}_m \sim p_r(\mathbf{x}), \bftheta_m \sim q(\bftheta|\bfpsi), \bfz_m \sim p(\bfz|\bftheta_m), \epsilon_m \sim U[0,1] \}_{m=1}^M$.}
                \For{$m=1$ to $M$}
                    \State{$\tilde{\mathbf{x}}_m \leftarrow g(\bfz_m; \bftheta_m)$}
                    \State{$\hat{\mathbf{x}}_m \leftarrow \epsilon_m \mathbf{x}_m + (1 - \epsilon_m) \tilde{\mathbf{x}}_m$}
                    \State{$U_d^{(m)} \leftarrow d(\tilde{\mathbf{x}}_m; \bfphi) - d(\mathbf{x}_m; \bfphi) + \lambda_{GP} (|| \nabla_{\hat{\mathbf{x}}_m} d(\hat{\mathbf{x}}_m; \bfphi) ||_2 - 1)^2 $}
                \EndFor
                \State{$\bfphi \leftarrow \text{Adam}(\nabla_\bfphi \tfrac{1}{M} \sum_{m=1}^M U_d^{(m)})$}
            \EndFor
            \State{Sample a mini-batch $\{ \bftheta_m \sim q(\bftheta|\bfpsi),  \bfz_m \sim p(\bfz|\bftheta_m) \}_{m=1}^M$.}  \Comment{Update $q(\bftheta|\bfpsi)$}
            \State{$\nabla_\bfpsi U_g \leftarrow \tfrac{1}{M} \sum_{m=1}^M -d(g(\bfz_m; \bftheta_m)) \nabla_\bfpsi \log q_\bfpsi(\bftheta_m)$}
            % \State{$\mathbf{F}(\bfpsi) \leftarrow \tfrac{1}{M} \sum_{m=1}^M  \nabla_\bfpsi \log q_\bfpsi(\bftheta_m) \nabla_\bfpsi \log q_\bfpsi(\bftheta_m)^{\top}$}
            \State{$\nabla_\bfpsi H(q_\bfpsi) \leftarrow \tfrac{1}{M} \sum_{m=1}^M  \nabla_\bfpsi q_\bfpsi(\bftheta_m) \log q_\bfpsi(\bftheta_m)$}
            \State{$\bfpsi \leftarrow \text{Adam}(\nabla_\bfpsi U_g + \gamma \nabla_\bfpsi H(q_\bfpsi))$}
        \EndWhile
    \end{algorithmic}
    \end{algorithm}
    \end{minipage}
\end{figure*}
